Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-11-13 bbbq_article.tex
Explain IEDB Method and Results better

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Peptide elution studies}\label{subsec:elution_studies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

To obtain experimental evidence that epitopes derived from TMHs are presented in MHC,
we used the Immune Epitope Database (IEDB) \cite{vita2019immune}.
This database contains the sequences of thousands of experimentally
established epitope sequences.
For each of these epitopes,
its possible location(s) in 
a human reference proteome,
with UniProt ID UP000005640\_9606, was mapped.
For the epitopes that were present in the proteome exactly once,
the topology of the proteins in which these epitopes were located 
was predicted using \verb;TMHMM; \cite{krogh2001predicting} . 
From this topology, we determined if the epitope
overlapped with a TMH.

@@

To obtain experimental confirmation that peptides stemming from TMHs 
are presented \emph{in vivo} in MHC-I and MHC-II,
we used epitope data from the IEDB.
We queried the IEDB for all linear epitopes obtained
from MHC ligand assays in healthy humans, 
for the MHC alleles as used in this study.
From these epitopes, we kept those that are found
exactly once in the human reference proteome.
We predicted the topology of the protein each epitope
was found in, using \verb;TMHMM; \cite{krogh2001predicting},
from which we conclude if the epitope is overlapping with a TMH
for at least 1 amino acid.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{TMH epitopes obtained from experimental data}\label{subsec:elution_studies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

To obtain experimental confirmation that peptides stemming from TMHs 
are presented \emph{in vivo} in MHC-I and MHC-II,
we used the Immune Epitope Database (IEDB) \cite{vita2019immune}.
We queried the IEDB for all linear epitopes obtained
from MHC ligand assays in healthy humans, 
for the MHC alleles as used in this study.
From these epitopes, we kept those that are found
exactly once in the human reference proteome
with UniProt ID UP000005640\_9606.
We predicted the topology of the protein each epitope
was found in, using \verb;TMHMM; \cite{krogh2001predicting},
from which we conclude if the epitope is overlapping with a TMH
for at least 1 amino acid.

@@

From the IEDB,
we obtained \richel{53,041}
and \richel{2,495} linear epitope sequences for our MHC-I 
and MHC-II alleles respectively.
There are relatively few epitopes for MHC-II, 
as MHC-II has many more different alleles than MHC-I \richel{describe how an
MHC-II allele is a combation of two alleles}, 
where we select only the 21 MHC-II alleles used in this study.

Figure \ref{fig:2a} shows that there is a correlation between the
percentage of TMH-derived epitopes that is presented \emph{in vivo}
versus the percentage of TMH-derived epitopes that is predicted to be presented
in MHC-I alleles. For MHC-II alleles, there were too few epitopes per MHC allele
to result in a useful plot.

We grouped all epitopes presented by MHC-I and MHC-II alleles and show 
the percentage of which these were TMH-derived in figure \ref{fig:2c}.
\richel{value}\% and \richel{value}\% were
predicted to be TMH-derived epitopes.
\richel{Indeed, what is the null hypothesis? The original one is that
zero percent of all TMH derived epitopes is presented, rendering statistics
useless. However, what about testing if TMH-derived epitopes are presented
just as often as TMHs are part of the proteom?}.
